Resilience and Home-Space for WSTS

### 2023-12-22 diapo/presentation.tex
up

\todo[inline,color=blue!20]{ {\it À l'oral~} 
\tiny We are usually focused on how to avoid bad states in general but you can see when your fridge the system stops providing refrigerating temperature it's not over yet
If you leave your fridge off for a minute it's not going to have Terrible impact but if you leave it off for more than one hour you're gonna have to throw the things in it away

@@

   Now we won't have time to detail all the result. 
   Result blabla are consequences of the paper    by Okzan so let's not delve into it.\\
   ( should still be quite precise about Okzan result)

    Let's delve into [This Result] in particular.

   Now recall the definitions ...

   \pause

@@

>>>>

  \todo[inline,color=blue!20]{ {\it À l'oral~}
We are usually focused on how to avoid bad states in general but you can see when your fridge the system stops providing refrigerating temperature it's not over yet
If you leave your fridge off for a minute it's not going to have Terrible impact but if you leave it off for more than one hour you're gonna have to throw the things in it away

@@

  \todo[inline,color=blue!20]{ {\it À l'oral~} 
   Now we won't have time to detail all the result. 
   Result blabla are consequences of the paper    by Okzan so let's not delve into it.
   }

    \todo[inline,color=blue!20]{  ( should still be quite precise about Okzan result and references)}

Result A

  \todo[inline,color=blue!20]{ {\it À l'oral~}   
    Let's delve into [This Result] in particular.

@@

	...}
